si: code and prose exploring Spatial Interaction models

### 2022-06-13 README.qmd
Remove final mentions of si?
Update readme #20

<!-- badges: start -->
[![R-CMD-check](https://github.com/Robinlovelace/sim/workflows/R-CMD-check/badge.svg)](https://github.com/Robinlovelace/sim/actions)
<!-- badges: end -->

The goal of {sim} is to provide a simple, [tidy](https://www.tidyverse.org/), and flexible framework for developing spatial interaction models (SIMs).
SIMs estimate the amount of movement between spatial entities and can be used for many things, including to support evidence-based investment in sustainable transport infrastructure and prioritisation of location options for public services.

Unlike many software tools designed to support spatial interaction modelling, {sim} does not define (or even encourage use of) any particular functional forms or modelling frameworks for predicting movement between origins and destinations.
Instead, it provides a framework enabling you to use model function forms or models of your choosing, ensuring flexibility and encouraging flexibility.

@@

```r
remotes::install_github("Robinlovelace/sim")
```

<!-- # Implementations in other languages -->
## si basics

@@

```{r distance}
library(sim)
library(dplyr)
# prepare OD data
od = si_to_od(
  origins = si_zones,        # origin locations
  destinations = si_zones,   # destination locations
  max_dist = 5000            # maximum distance between OD pairs
  )
# specify a function
gravity_model = function(beta, d, m, n) {
  m * n * exp(-beta * d / 1000)
} 
# perform SIM
od_res = si_calculate(
  od,
  fun = gravity_model,
  d = distance_euclidean,
  m = origin_all,
  n = destination_all,
  constraint_production = origin_all,
  beta = 0.9
  )
# visualize the results
plot(od_res$distance_euclidean, od_res$interaction)
```

@@

The approach is also 'tidy', allowing use of {sim} functions in {dplyr} pipelines:

@@

As documented in the [si vignette](https://robinlovelace.github.io/si/articles/si.html), the function allows you to use any variable in the origin or destination data by joining all attributes onto the OD data frame, with column names appended with `origin` and `destination`.

@@

For details on what SIMs are and how they have been defined mathematically and in code from first principles, see the [`sims` vignette](https://robinlovelace.github.io/si/articles/sims-first-principles.html).

To dive straight into using {sim} to develop SIMs, see the [`si` Get started vignette](https://robinlovelace.github.io/si/articles/si.html).

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/robinlovelace/simodels/workflows/R-CMD-check/badge.svg)](https://github.com/robinlovelace/simodels/actions)
<!-- badges: end -->

The goal of {simodels} is to provide a simple, [tidy](https://www.tidyverse.org/), and flexible framework for developing spatial interaction models (SIMs).
SIMs estimate the amount of movement between spatial entities and can be used for many things, including to support evidence-based investment in sustainable transport infrastructure and prioritisation of location options for public services.

Unlike many software tools designed to support spatial interaction modelling, {simodels} does not define (or even encourage use of) any particular functional forms or modelling frameworks for predicting movement between origins and destinations.
Instead, it provides a framework enabling you to use model function forms or models of your choosing, ensuring flexibility and encouraging flexibility.

@@

```r
remotes::install_github("robinlovelace/simodels")
```

<!-- # Implementations in other languages -->
## simodel basics

@@

```{r distance}
library(simodels)
library(dplyr)
# prepare OD data
od = si_to_od(
  origins = si_zones,        # origin locations
  destinations = si_zones,   # destination locations
  max_dist = 5000            # maximum distance between OD pairs
  )
# specify a function
gravity_model = function(beta, d, m, n) {
  m * n * exp(-beta * d / 1000)
} 
# perform SIM
od_res = si_calculate(
  od,
  fun = gravity_model,
  d = distance_euclidean,
  m = origin_all,
  n = destination_all,
  constraint_production = origin_all,
  beta = 0.9
  )
# visualize the results
plot(od_res$distance_euclidean, od_res$interaction)
```

@@

The approach is also 'tidy', allowing use of {simodels} functions in {dplyr} pipelines:

@@

The function allows you to use any variable in the origin or destination data by joining all attributes onto the OD data frame, with column names appended with `origin` and `destination`.

@@

For details on what SIMs are and how they have been defined mathematically and in code from first principles, see the [`sims` vignette](https://robinlovelace.github.io/simodels/articles/sims-first-principles.html).

To dive straight into using {simodels} to develop SIMs, see the [`si` Get started vignette](https://robinlovelace.github.io/simodels/articles/si.html).
